---
title: "DPH data analysis"
author: "Lyubava Erko"
date: "10/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = FALSE, echo = FALSE, warning = FALSE}
library(mgcv)
library(goft)
library(car)
library(performance)
library(DHARMa)
library(fitdistrplus)
library(gamlss)
library(tidyverse)
library(here)
library(dplyr)
```
# loading the cvs files

```{r}
lorazepam = read_csv(here("E:/Lyubava_UVic/Term 4 (Bamfield)/DS/GitHub/Lorazepam acute.csv")) %>%
    mutate(percentile = as.factor(percentile), time_min = as.factor(time_min)) 
DPH_acute = read_csv(here("E:/Lyubava_UVic/Term 4 (Bamfield)/DS/GitHub/DPH acute.csv")) %>%
    mutate(percentile = as.factor(percentile), time_min = as.factor(time_min)) 

DPH_chronic <- read_delim("E:/Lyubava_UVic/Term 4 (Bamfield)/DS/GitHub/DPH chronic.csv", delim = ',') %>%
    mutate(percentile = as.factor(percentile), time_min = as.factor(time_min)) 
```
      _______________________________
# DPH acute graphs
## 0-50 proportion

```{r}
DPH_acute_0_50 <- DPH_acute %>%
  filter(percentile == "0-25" | percentile == "25-50") %>%
  group_by(time_min, treatment, replicate_number) %>%
  mutate(proportion_light = sum(proportion))
```


```{r}
ggplot(DPH_acute_0_50, aes(x = time_min,
                           y = proportion_light,
                           colour = treatment,
                           fill=treatment)) +
  geom_point() +
  theme_classic()+
  geom_smooth(method="glm") +
  xlab ("time(min)") +
  ylab ("copepod proportion")
```


## 50-100 proportion

```{r}
DPH_acute_50_100 <- DPH_acute %>%
  filter(percentile == "50-75" | percentile == "75-100") %>%
  group_by(time_min, treatment, replicate_number) %>%
  mutate(proportion_light = sum(proportion))
```


```{r}
ggplot(DPH_acute_50_100, aes(x = time_min,
                           y = proportion_light,
                           colour = treatment,
                           fill=treatment)) +
  geom_point() +
  theme_classic()+
  geom_smooth(method="glm") +
  xlab ("time(min)") +
  ylab ("copepod proportion")
```
____________________________________________________________________________________

#look at shapiro test for normality because we have count data/ proportion data (gamma distribution), which is often non-normal. See ppt slides on topic 6. 
Use beta distribution for proportion data. Gamma might also work.Use desk disc fnbction and do hist discs + fit disc function most importantly.
Do mutate function to have a proportion from 0 to 1.
Turn percentile column into a factor.

Try binomial distribution for percentiles 1 and 2, and 3 and 4. Include the biological effect. 
____________________________________________________________________________________

      ______________________

## DPH chronic

## 0-50 proportion

```{r}
DPH_chronic_0_50 <- DPH_chronic %>%
  filter(percentile == "0-25" | percentile == "25-50") %>%
  group_by(time_min, treatment, replicate_number) %>%
  mutate(proportion_light = sum(proportion))
```


```{r}
ggplot(DPH_chronic_0_50, aes(x = time_min,
                           y = proportion_light,
                           colour = treatment,
                           fill=treatment)) +
  geom_point() +
  theme_classic()+
  geom_smooth(method="glm") +
  xlab ("time(min)") +
  ylab ("copepod proportion")
```
## 50-100 proportion

```{r}
DPH_chronic_50_100 <- DPH_chronic %>%
  filter(percentile == "50-75" | percentile == "75-100") %>%
  group_by(time_min, treatment, replicate_number) %>%
  mutate(proportion_light = sum(proportion))
```


```{r}
ggplot(DPH_chronic_50_100, aes(x = time_min,
                           y = proportion_light,
                           colour = treatment,
                           fill=treatment)) +
  geom_point() +
  theme_classic()+
  geom_smooth(method="glm") +
  xlab ("time(min)") +
  ylab ("copepod proportion")
```
      ______________________

## Lorazepam acute


## 0-50 proportion

```{r}
lorazepam_acute_0_50 <- lorazepam %>%
  filter(percentile == "0-25" | percentile == "25-50") %>%
  group_by(time_min, treatment, replicate_number) %>%
  mutate(proportion_light = sum(proportion))
```


```{r}
ggplot(lorazepam_acute_0_50, aes(x = time_min,
                           y = proportion_light,
                           colour = treatment,
                           fill=treatment)) +
  geom_point() +
  theme_classic()+
  geom_smooth(method="glm") +
  xlab ("time(min)") +
  ylab ("copepod proportion")
```
## 50-100 proportion

```{r}
lorazepam_acute_50_100 <- lorazepam %>%
  filter(percentile == "50-75" | percentile == "75-100") %>%
  group_by(time_min, treatment, replicate_number) %>%
  mutate(proportion_light = sum(proportion))
```


```{r}
ggplot(lorazepam_acute_50_100, aes(x = time_min,
                           y = proportion_light,
                           colour = treatment,
                           fill=treatment)) +
  geom_point() +
  theme_classic()+
  geom_smooth(method="glm") +
  xlab ("time(min)") +
  ylab ("copepod proportion")
```





