---
title: "DPH data analysis"
author: "Lyubava Erko"
date: "10/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = FALSE, echo = FALSE, warning = FALSE}
library(mgcv)
library(goft)
library(car)
library(performance)
library(DHARMa)
library(fitdistrplus)
library(gamlss)
library(tidyverse)
library(here)
library(dplyr)
library(MASS)
library(patchwork)
```
# loading the cvs files

Backup
```{r}
lorazepam = read_csv(here("./Data/DS copepod data - Lorazepam acute.csv")) %>%
    mutate(percentile = as.factor(percentile), time_min = as.factor(time_min)) 

DPH_acute = read_csv(here("./Data/DS copepod data - DPH acute_right one.csv")) %>%
    mutate(percentile = as.factor(percentile), time_min = as.factor(time_min))

DPH_chronic = read_csv(here("./Data/DS copepod data - DPH chronic.csv")) %>%
    mutate(percentile = as.factor(percentile), time_min = as.factor(time_min))
```
      _______________________________
# DPH acute graphs
## 0-50 proportion

```{r}
DPH_acute_0_50 <- DPH_acute %>%
  filter(percentile == "0-25" | percentile == "25-50") %>%
  group_by(time_min, treatment, replicate_number) %>%
  summarize(proportion_light = sum(proportion))
```
```{r}
p1 = ggplot(DPH_acute_0_50, aes(x = time_min,
                           y = proportion_light,
                           fill = treatment)) +
  geom_boxplot(alpha = 0.8) +
  labs(x = "Treatment", y = "Proportion of copepods") +
  ylim(0, 0.8) +
  ggtitle("A. DPH acute exposure for covered top") +
  theme_classic()+
  labs(fill = "Treatment") +
  scale_fill_manual(labels = c("Control", "Environmentally relevant", "High"), values = c("skyblue1", "palegreen3", "firebrick1"))

plot(p1)
```



## 50-100 proportion

```{r}
DPH_acute_50_100 <- DPH_acute %>%
  filter(percentile == "50-75" | percentile == "75-100") %>%
  group_by(time_min, treatment, replicate_number) %>%
  summarize(proportion_light = sum(proportion))
```


```{r}
p2 = ggplot(DPH_acute_50_100, aes(x = time_min,
                           y = proportion_light,
                           fill = treatment)) +
  geom_boxplot(alpha = 0.8) +
  labs(x = "Treatment", y = "Proportion of copepods") +
  ylim(0, 0.8) +
  ggtitle("B. DPH acute exposure for covered bottom") +
  theme_classic()+
  labs(fill = "Treatment") +
  scale_fill_manual(labels = c("Control", "Environmentally relevant", "High"), values = c("skyblue1", "palegreen3", "firebrick1"))

plot(p2)
```
____________________________________________________________________________________

#look at shapiro test for normality because we have count data/ proportion data (gamma distribution), which is often non-normal. See ppt slides on topic 6. 
Use beta distribution for proportion data. Gamma might also work.Use desk disc fnbction and do hist discs + fit disc function most importantly.
Do mutate function to have a proportion from 0 to 1.
Turn percentile column into a factor.

Try binomial distribution for percentiles 1 and 2, and 3 and 4. Include the biological effect. 
____________________________________________________________________________________

      ______________________

## DPH chronic

## 0-50 proportion

```{r}
DPH_chronic_0_50 <- DPH_acute %>%
  filter(percentile == "0-25" | percentile == "25-50") %>%
  group_by(time_min, treatment, replicate_number) %>%
  summarize(proportion_light = sum(proportion))
```


```{r}
p3 = ggplot(DPH_chronic_0_50, aes(x = time_min,
                           y = proportion_light,
                           fill = treatment)) +
  geom_boxplot(alpha = 0.8) +
  labs(x = "Treatment", y = "Proportion of copepods") +
  ylim(0, 0.8) +
  ggtitle("C. DPH chronic exposure for covered top") +
  theme_classic()+
  labs(fill = "Treatment") +
  scale_fill_manual(labels = c("Control", "Environmentally relevant", "High"), values = c("skyblue1", "palegreen3", "firebrick1"))

plot(p3)
```

## 50-100 proportion

```{r}
DPH_chronic_50_100 <- DPH_chronic %>%
  filter(percentile == "50-75" | percentile == "75-100") %>%
  group_by(time_min, treatment, replicate_number) %>%
  summarize(proportion_light = sum(proportion))
```


```{r}
p4 = ggplot(DPH_chronic_50_100, aes(x = time_min,
                           y = proportion_light,
                           fill = treatment)) +
  geom_boxplot(alpha = 0.8) +
  labs(x = "Treatment", y = "Proportion of copepods") +
  ylim(0, 0.8) +
  ggtitle("D. DPH chronic exposure for covered bottom") +
  theme_classic()+
  labs(fill = "Treatment") +
  scale_fill_manual(labels = c("Control", "Environmentally relevant", "High"), values = c("skyblue1", "palegreen3", "firebrick1"))

plot(p4)
```
      ______________________

## Lorazepam acute


## 0-50 proportion

```{r}
lorazepam_acute_0_50 <- lorazepam %>%
  filter(percentile == "0-25" | percentile == "25-50") %>%
  group_by(time_min, treatment, replicate_number) %>%
  summarize(proportion_light = sum(proportion))
```


```{r}
p5 = ggplot(lorazepam_acute_0_50, aes(x = time_min,
                           y = proportion_light,
                           fill = treatment)) +
  geom_boxplot(alpha = 0.8) +
  labs(x = "Treatment", y = "Proportion of copepods") +
  ylim(0, 0.8) +
  ggtitle("A. Lorazepam acute exposure for covered top") +
  theme_classic()+
  labs(fill = "Treatment") +
  scale_fill_manual(labels = c("Control", "Environmentally relevant", "High"), values = c("skyblue1", "palegreen3", "firebrick1"))

plot(p5)
```
## 50-100 proportion


```{r}
lorazepam_acute_50_100 <- lorazepam %>%
  filter(percentile == "50-75" | percentile == "75-100") %>%
  group_by(time_min, treatment, replicate_number) %>%
  summarize(proportion_light = sum(proportion))
```


```{r}
p6 = ggplot(lorazepam_acute_50_100, aes(x = time_min,
                           y = proportion_light,
                           fill = treatment)) +
  geom_boxplot(alpha = 0.8) +
  labs(x = "Treatment", y = "Proportion of copepods") +
  ylim(0, 0.8) +
  ggtitle("B. Lorazepam acute exposure for covered bottom") +
  theme_classic()+
  labs(fill = "Treatment") +
  scale_fill_manual(labels = c("Control", "Environmentally relevant", "High"), values = c("skyblue1", "palegreen3", "firebrick1"))

plot(p6)
```

```{r}
(p1 / p3) | (p2/p4)

```
```{r}
p5 | p6

```




